\sectionHeader{EXPERIENCE}

\flushleft \begin{minipage}[t]{\dateColWidth}
Fall 2013 \\
(4 Months)
\end{minipage}
\begin{minipage}[t]{0.8\textwidth}
	\mysubsection{Design of a Mechanical Governor -- AME 408 Final Project}
	--
	Managed team to design a rotating governor part, given deformation and natural frequency requirements using SolidWorks. 
	
	Tags:
	\tag{Leadership} \vline\ 
	\tag{Teamwork} \vline\
	\tag{SolidWorks} \vline\
	\tag{CAD} \vline\
	\tag{FEA}
	--
	\href{http://claytonketner.com/cad-at-a-glance/}{\uline{\textit{more info}}}
\end{minipage}

\divLine

\flushleft \begin{minipage}[t]{\dateColWidth}
Fall 2012 \\
(4 Months)
\end{minipage}
\begin{minipage}[t]{0.8\textwidth}
	\mysubsection{Senior Project -- Remote Inspection Vehicle}
	--
	Remote control robot for the 2013 ASME design competition. Designed and built the controller. Coded and wired the controller and robot.

	Tags:
	\tag{CAD} \vline\ 
	\tag{DESIGN} \vline\ 
	\tag{LEADERSHIP} \vline\ 
	\tag{CODE} \vline\ 
	\tag{WIRELESS} \vline\ 
	\tag{ROBOTICS}
	--
	\href{http://www.claytonketner.com/senior-project-robot/}{\uline{\textit{more info}}}
\end{minipage}

\divLine

% Col 1
\flushleft \begin{minipage}[t]{\dateColWidth}
Summer 2012 \\
(2 Months)
\end{minipage}
% Col 2
\begin{minipage}[t]{0.8\textwidth}
	\mysubsection{Robotic Arm}
	--
	Designed, manufactured, wired, and coded independently and from scratch.
	\\[0.2 em]
	Tags: 
	\tag{CAD} \vline\ 
	\tag{CNC} \vline\ 
	\tag{DESIGN} \vline\ 
	\tag{FABRICATION} \vline\ 
	\tag{CODE} \vline\ 
	\tag{MATLAB} \vline\ 
	\tag{ROBOTICS}
	--
	\href{http://www.claytonketner.com/robotic-arm-mk2/}{\uline{\textit{more info}}}
\end{minipage}

\divLine

\flushleft \begin{minipage}[t]{\dateColWidth}
Summer 2011 \\
(3 Months)
\end{minipage}
\begin{minipage}[t]{0.8\textwidth}
\mysubsection{OSIsoft -- Virtual Campus Intern} (40 hr/wk) \\[-1 em]
\begin{adjustwidth}{2.5 em}{0 em} 

\begin{itemize} \itemsep-2pt
\setlength{\itemindent}{-2 em}

\item Independently researched \& integrated OSIsoft PI System with SAS analytics.
\item Gave two live progress presentations to the Virtual Campus team.
\item Concluded findings in a White Paper posted to OSIsoft's vCampus website.
\item\textbf{Received praise from an outside company for quality of the White Paper.}
\end{itemize}

\end{adjustwidth}
\end{minipage}